### 2023-11-06 manuscript/manuscript.Rmd
Correct table 2 caption.

standards_compound_outcomes %>%
  dplyr::mutate(
    outcome = outcome %>%
      stringr::str_replace_all(
        'm/z',
        '\\\\textit{m/z}'
      ) %>% 
      stringr::str_replace_all(
        '&',
        '\\\\&'
      )
  ) %>%
  dplyr::relocate(
    spiked_urine,
    .after = dplyr::everything()
  ) %>%
  dplyr::rename(
    ` ` = outcome,
    `Standards mix` = standards,
    `Spiked urine` = spiked_urine
  ) %>%
  kableExtra::kable(
    format = 'latex',
    booktabs = TRUE,
    escape = FALSE,
    linesep = '',
    align = c(
      rep('l',1),
      rep('r',2)
    ),
    caption = 'Assignments results frequencies for the 64 unique molecular formulas of the chemical standards in the standards mix and spiked into human urine.'
  ) %>%
  kableExtra::kable_styling(
    latex_options = "HOLD_position"
  )
```

>>>>

standards_compound_outcomes %>%
  dplyr::mutate(
    outcome = outcome %>%
      stringr::str_replace_all(
        'm/z',
        '\\\\textit{m/z}'
      ) %>% 
      stringr::str_replace_all(
        '&',
        '\\\\&'
      )
  ) %>%
  dplyr::relocate(
    spiked_urine,
    .after = dplyr::everything()
  ) %>%
  dplyr::rename(
    ` ` = outcome,
    `Standards mix` = standards,
    `Spiked urine` = spiked_urine
  ) %>%
  kableExtra::kable(
    format = 'latex',
    booktabs = TRUE,
    escape = FALSE,
    linesep = '',
    align = c(
      rep('l',1),
      rep('r',2)
    ),
    caption = 'Molecular formula assignment results frequencies for the 64 unique molecular formulas of the chemical standards in the standards mix and spiked into human urine.'
  ) %>%
  kableExtra::kable_styling(
    latex_options = "HOLD_position"
  )
```
